\begin{thebibliography}{9}	
\addcontentsline{toc}{chapter}{\bibname}
\large

\bibitem{NPCOMP} R.L. Graham, E.L. Lawler, J.K. Lenstra и A.H.G.Rinnooy Kan. «Optimization and Approximation in Deterministic Sequencing and Scheduling: a Survey». В: Discrete Optimization
17
IIProceedings of the Advanced Research Institute on Discrete Optimization and Systems Applications of the Systems Science Panel of NATO and of the Discrete Optimization Symposium co-sponsored by IBM Canada and SIAM Banff, Aha. and Vancouver. Под ред. E.L. Johnson P.L. Hammer и B.H. Korte. Т. 5. Annals of Discrete Mathematics. Elsevier, 1979, с. 287—326. doi: \url{http://dx.doi.org/10.1016/S0167-5060(08)70356- X}. url: \url{http://www.sciencedirect.com/science/article/pii/S016750600870356X}.

%\bibitem{NZOV} Назаренко Алексей, такой-то год такое-то издание.

\bibitem{DLS} G. C. Sih и E. A. Lee. «Dynamic-level scheduling for heterogeneous processor networks». В: Parallel and Distributed Processing, 1990. Proceedings of the Second IEEE Symposium on. Дек. 1990, с. 42—49. doi: \href{http://ieeexplore.ieee.org/document/143505/}{10.1109/SPDP.1990.143505}


\bibitem{HEFT} H. Topcuoglu, S. Hariri и Min-You Wu. «Task scheduling algorithms for heterogeneous processors». В: Heterogeneous Computing Workshop, 1999. (HCW ’99) Proceedings. Eighth. 1999, с. 3—14. doi: \href{http://ieeexplore.ieee.org/document/765092/}{10.1109/HCW.1999.765092}

\bibitem{GA} Lee Wang, Howard Jay Siegel, Vwani P. Roychowdhury и Anthony A. Maciejewski. «Task Matching and Scheduling in Heterogeneous Computing Environments Using a Genetic- Algorithm-Based Approach». В: J. Parallel Distrib. Comput. 47.1 (нояб. 1997), с. 8—22. issn: 0743-7315. url: \url{http://dx.doi.org/10.1006/ jpdc.1997.1392}

\bibitem{GIT} [HTTP] \href{https://github.com/alexmnazarenko/pysimgrid}{https://github.com/alexmnazarenko/pysimgrid}


\end{thebibliography}